Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-14 paper/arxiv/supp_3_ml.tex
fix quote signs

The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{supp_fig20:input_dos}.
Here, "numSamplings" represents the number of data points sampled across the energy spectrum,
"numOrbitals" denotes the number of DOS orbitals,
and "numChannels" indicates the number of atomic channels.

@@

% Supplementary Table 16: The hyperparameter search space
\begin{table}[htbp]
  \centering
  \begin{tabular}{llp{5cm}}
    \toprule
    Hyperparameter& Search Space              & Description                                                       \\
    \midrule
    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam \cite{kingma2017adam} optimizer \\
    dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
    root\_fc0     & 128, 256, 512             & Output dimensionality of 1\textsuperscript{st} fully connected layer in root           \\
    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root           \\
    root\_act     & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in root             \\
    kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
    numFilters    & [8, 64]                   & Number of filters in the convolution                              \\
    numConvLayers & [1, 16]                   & Number of convolution layers                                      \\
    numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch      \\
    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch      \\
    br\_act       & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in branch           \\
    \bottomrule
  \end{tabular}
  \caption{The hyperparameter search space}
  \label{supp_table16:hyperparam_space}
\end{table}

% Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
\begin{table}[htbp]
  \centering
  \begin{tabular}{llp{6cm}}
    \toprule
    Hyperparameter& Optimal Value & Description                                              \\
    \midrule
    learningRate  & $10^{-3}$ & Learning rate of Adam \cite{kingma2017adam} optimizer                              \\
    dropoutRate   & 0.3       & Dropout rate                                                 \\
    root\_fc0     & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in root   \\
    root\_fc1     & 512       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root   \\
    root\_act     & "relu"    & Activation function of fully connected layers in root        \\
    kernelSize    & 10        & Width of convolution window                                  \\
    numFilters    & 17        & Number of filters in the convolution                         \\
    numConvLayers & 3         & Number of convolution layers                                 \\
    numConvBlocks & 1         & Number of convolution blocks                                 \\
    br\_fc0       & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch \\
    br\_fc1       & 128       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch \\
    br\_act       & "tanh"    & Activation function of fully connected layers in branch      \\
    \bottomrule
  \end{tabular}
  \caption{Optimal hyperparameters identified with Hyperband algorithm}
  \label{supp_table17:opt_hyperparam}
\end{table}

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
  \centering
  \begin{tabular}{lll}
    \toprule
    Adsorbate             & Original dataset (eV)  & Augmented dataset (eV)  \\
    \midrule
    CO\textsubscript{2}   & 0.0447                 & 0.0336                  \\
    COOH                  & 0.0436                 & 0.0581                  \\
    CO                    & 0.0402                 & 0.0402                  \\
    CHO                   & 0.0614                 & 0.0778                  \\
    CH\textsubscript{2}O  & 0.0553                 & 0.0632                  \\
    OCH\textsubscript{3}  & 0.0605                 & 0.0636                  \\
    O                     & 0.1135                 & 0.1081                  \\
    OH                    & 0.0547                 & 0.0602                  \\
    H                     & 0.0703                 & 0.0646                  \\
    \bottomrule
  \end{tabular}
  \caption{Prediction mean absolute errors of the CNN model}
  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
  The term "original dataset" refers to evaluations conducted on the original dataset without any augmented data;
  it does not imply the use of a different CNN model trained solely on the original dataset.
  Similarly, "augmented dataset" refers to evaluations on the dataset with both original data and augment data,
  not a distinct model.}
  \label{supp_table18:cnn_mae}
\end{table}

@@

% SI Figure 21: Illustration of the eDOS occlusion experiment
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig21_occlusion.png}
  \caption{\textbf{Illustration of the eDOS occlusion experiment.}
  This figure demonstrates the step-by-step process of the occlusion experiment.
  The input eDOS array first undergoes zero-padded, and then a masker of width "width" is applied,
  resulting in an occlusion array that preserves the shape of the input array.}
  \label{supp_fig21:occlusion}
\end{figure}

% SI Figure 22: Occlusion experiment with a masker width of 1
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig22_occl_wid1.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "1".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig22:occl_wid1}
\end{figure}

% SI Figure 23: Occlusion experiment with a masker width of 3
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig23_occl_wid3.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "3".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig23:occl_wid3}
\end{figure}

% SI Figure 24: Occlusion experiment with a masker width of 5
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig24_occl_wid5.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "5".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig24:occl_wid5}
\end{figure}

% SI Figure 25: Occlusion experiment with a masker width of 11
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig25_occl_wid11.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "11".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig25:occl_wid11}
\end{figure}

% SI Figure 26: Occlusion experiment with a masker width of 21
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig26_occl_wid21.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "21".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig26:occl_wid21}
\end{figure}

% SI Figure 27: Occlusion experiment with a masker width of 31
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig27_occl_wid31.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "31".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig27:occl_wid31}
\end{figure}

% SI Figure 28: Occlusion experiment with a masker width of 41
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig28_occl_wid41.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "41".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig28:occl_wid41}
\end{figure}

% SI Figure 29: Occlusion experiment with a masker width of 51
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig29_occl_wid51.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "51".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig29:occl_wid51}
\end{figure}

>>>>

The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{supp_fig20:input_dos}.
Here, ``numSamplings'' represents the number of data points sampled across the energy spectrum,
``numOrbitals'' denotes the number of DOS orbitals,
and ``numChannels'' indicates the number of atomic channels.

@@

% Supplementary Table 16: The hyperparameter search space
\begin{table}[htbp]
  \centering
  \begin{tabular}{llp{5cm}}
    \toprule
    Hyperparameter& Search Space              & Description                                                       \\
    \midrule
    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam \cite{kingma2017adam} optimizer \\
    dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
    root\_fc0     & 128, 256, 512             & Output dimensionality of 1\textsuperscript{st} fully connected layer in root           \\
    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root           \\
    root\_act     & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in root             \\
    kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
    numFilters    & [8, 64]                   & Number of filters in the convolution                              \\
    numConvLayers & [1, 16]                   & Number of convolution layers                                      \\
    numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch      \\
    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch      \\
    br\_act       & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in branch           \\
    \bottomrule
  \end{tabular}
  \caption{The hyperparameter search space}
  \label{supp_table16:hyperparam_space}
\end{table}

% Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
\begin{table}[htbp]
  \centering
  \begin{tabular}{llp{6cm}}
    \toprule
    Hyperparameter& Optimal Value & Description                                              \\
    \midrule
    learningRate  & $10^{-3}$ & Learning rate of Adam \cite{kingma2017adam} optimizer                              \\
    dropoutRate   & 0.3       & Dropout rate                                                 \\
    root\_fc0     & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in root   \\
    root\_fc1     & 512       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root   \\
    root\_act     & ``relu''    & Activation function of fully connected layers in root        \\
    kernelSize    & 10        & Width of convolution window                                  \\
    numFilters    & 17        & Number of filters in the convolution                         \\
    numConvLayers & 3         & Number of convolution layers                                 \\
    numConvBlocks & 1         & Number of convolution blocks                                 \\
    br\_fc0       & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch \\
    br\_fc1       & 128       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch \\
    br\_act       & ``tanh''    & Activation function of fully connected layers in branch      \\
    \bottomrule
  \end{tabular}
  \caption{Optimal hyperparameters identified with Hyperband algorithm}
  \label{supp_table17:opt_hyperparam}
\end{table}

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
  \centering
  \begin{tabular}{lll}
    \toprule
    Adsorbate             & Original dataset (eV)  & Augmented dataset (eV)  \\
    \midrule
    CO\textsubscript{2}   & 0.0447                 & 0.0336                  \\
    COOH                  & 0.0436                 & 0.0581                  \\
    CO                    & 0.0402                 & 0.0402                  \\
    CHO                   & 0.0614                 & 0.0778                  \\
    CH\textsubscript{2}O  & 0.0553                 & 0.0632                  \\
    OCH\textsubscript{3}  & 0.0605                 & 0.0636                  \\
    O                     & 0.1135                 & 0.1081                  \\
    OH                    & 0.0547                 & 0.0602                  \\
    H                     & 0.0703                 & 0.0646                  \\
    \bottomrule
  \end{tabular}
  \caption{Prediction mean absolute errors of the CNN model}
  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
  The term ``original dataset'' refers to evaluations conducted on the original dataset without any augmented data;
  it does not imply the use of a different CNN model trained solely on the original dataset.
  Similarly, ``augmented dataset'' refers to evaluations on the dataset with both original data and augment data,
  not a distinct model.}
  \label{supp_table18:cnn_mae}
\end{table}

@@

% SI Figure 21: Illustration of the eDOS occlusion experiment
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig21_occlusion.png}
  \caption{\textbf{Illustration of the eDOS occlusion experiment.}
  This figure demonstrates the step-by-step process of the occlusion experiment.
  The input eDOS array first undergoes zero-padded, and then a masker of width ``width'' is applied,
  resulting in an occlusion array that preserves the shape of the input array.}
  \label{supp_fig21:occlusion}
\end{figure}

% SI Figure 22: Occlusion experiment with a masker width of 1
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig22_occl_wid1.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``1''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig22:occl_wid1}
\end{figure}

% SI Figure 23: Occlusion experiment with a masker width of 3
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig23_occl_wid3.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``3''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig23:occl_wid3}
\end{figure}

% SI Figure 24: Occlusion experiment with a masker width of 5
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig24_occl_wid5.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``5''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig24:occl_wid5}
\end{figure}

% SI Figure 25: Occlusion experiment with a masker width of 11
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig25_occl_wid11.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``11''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig25:occl_wid11}
\end{figure}

% SI Figure 26: Occlusion experiment with a masker width of 21
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig26_occl_wid21.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``21''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig26:occl_wid21}
\end{figure}

% SI Figure 27: Occlusion experiment with a masker width of 31
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig27_occl_wid31.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``31''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig27:occl_wid31}
\end{figure}

% SI Figure 28: Occlusion experiment with a masker width of 41
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig28_occl_wid41.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``41''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig28:occl_wid41}
\end{figure}

% SI Figure 29: Occlusion experiment with a masker width of 51
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig29_occl_wid51.png}
  \caption{\textbf{Occlusion Experiment with a masker width of ``51''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig29:occl_wid51}
\end{figure}
